OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-03-22 paper/paper.Rmd
Give context for ref clustering against DBs

**TODO: lead with comparison of optifit vs current state of the art. give context at beginning.**
We performed _de novo_ clustering with OptiClust at distance threshold of 3%
using the Greengenes database, SILVA non-redundant database, or the Ribosomal
Database Project (RDP) [@desantis_greengenes_2006; @quast_silva_2013;
@cole_ribosomal_2014].
We then performed refernce clustering with OptiFit, fitting each dataset to each 
set of database OTUs repeated 100 times.
We measured the algorithm run time and evaluated OTU quality using the MCC as
described previously [@westcott_opticlust_2017].
To compare to existing software, we also clustered each dataset into _de novo_
OTUs  using OptiClust and VSEARCH, and with VSEARCH in reference-based mode
against the Greengenes database.

>>>>

While _de novo_ clustering produces high quality OTUs, researchers may prefer to
perform reference clustering to a public database because reference-based
methods produce stable OTUs and are generally faster than _de novo_ methods.
To test how OptiFit performs for this purpose, we fit each dataset to three
databases of reference OTUs; the Greengenes database, the SILVA non-redundant
database, and the Ribosomal Database Project (RDP) [@desantis_greengenes_2006;
@quast_silva_2013; @cole_ribosomal_2014].
Reference OTUs for each database were created by performing _de novo_ clustering
with OptiClust at a distance threshold of 3%.
To compare to existing software, we also clustered each dataset into _de novo_
OTUs using OptiClust and VSEARCH, and with VSEARCH in reference-based mode
against the Greengenes database of OTUs clustered at 97% similarity.
